Price of Anarchy for Mean Field Games

### 2018-07-25 PoA.tex
edits, and mistake found in Proposition 4!
fixed mistake in prop 4

% proposition b_2 to \infty
\begin{proposition}
	Assuming (\ref{eq:assumptions}), $q_T+\bar{q}_T(1-s_T)>0$, $q_T+\bar{q}_T(1-s_T)^2>0$, and the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, then:
	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
\label{prop:b2_to_infty}
\end{proposition}

@@

\begin{proof}
	When $b_2 \to \infty$, we have:
	\begin{equation*}
	\begin{array}{l}
	\lambda^{b_2} \to \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}, \\
	B^{b_2} \to \infty, \qquad B^{\eta,b_2} \to \infty\\
	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty},
	\end{array}
	\end{equation*}
	and $A^{u}, (A^{w}, C^w, D^w), (A^{\eta}, C^{\eta}, D^{\eta})$ are independent of  $b_2$. Moreover, we notice that:
	\begin{equation*}
		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} = -\frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{(A^u)^2}{(b_2+\bar{b}_2)^2}+\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \xrightarrow[b_2 \to \infty]{} \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}}.
	\end{equation*}
	and thus, $\delta^{+,b_2}_u - \delta^{-,b_2}_u \xrightarrow[b_2 \to \infty]{} +\infty$.
	From the assumption $q_T+\bar{q}_T(1-s_T)>0$, we have $D^u>0$. From equation (\ref{eq:riccati_ut_sol}), for each $t \in[0,T)$, we deduce:
	\begin{IEEEeqnarray*}{rCl}
		(b_2 + \bar{b}_2) u^{b_2}_t &=& \frac{ \displaystyle  \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{+,b_2}_u}{b_2 + \bar{b}_2}\right) - \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{-,b_2}_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} }
		{\displaystyle \left(\frac{- \delta^{-,b_2}_u}{(b_2 + \bar{b}_2)^2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} \right) + \left(\frac{\delta^{+,b_2}_u}{(b_2 + \bar{b}_2)^2} - \frac{D^{u,b_2} }{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)}  } \nonumber \\
		&&\\
		&\xrightarrow[b_2 \to \infty]{}& \quad (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_u^{b_2 \to \infty}}  =: c_u
	\end{IEEEeqnarray*}
	Idem, for any $t \in [0,T)$,
	$$ (b_2 + \bar{b}_2) w_t^{b_2} \xrightarrow[b_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} = \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} }.$$
%	and for any $t \in [0,T)$,
%	$$ b_2 \eta_t^{b_2} \xrightarrow[b_2 \to \infty]{} (r+ \bar{r}) c_{\delta_\eta^{b_2 \to \infty}} =: c_5, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} = \sqrt{\frac{q+\bar{q}}{r + \bar{r}}}.
%	$$

@@

	Fix $\epsilon>0$. In the following, we show that the time point $t^*$ can be chosen such that $I_1^{b_2} \leq \epsilon$ and $I_2^{b_2} \leq \epsilon$ for large $b_2$.

	% the term I_1
	First, consider $I_1^{b_2}$. Recall that for $t \in[0,T/2]$, we have $\lim_{b_2 \to \infty}h_u(b_2,t) = c_u$ and $\lim_{b_2 \to \infty}h_w(b_2,t) = c_w$, and for all $b_2 \geq b_2^{*,upper}$, the functions $[0,T/2] \ni s \mapsto u_s^{b_2}$ and $[0,T/2] \ni s \mapsto w_s^{b_2}$ are increasing, and thus, $[0,T/2] \ni s \mapsto h_u(b_2,t)$ and $[0,T/2] \ni s \mapsto h_w(b_2,t)$ are increasing. (Note that $T/2<T$ is chosen arbitrarily, since the above limits do not hold at $T$.) Let $\zeta_2 =\frac{1}{2} \min \{ c_u, c_w \} $. Then there exists $b_2^{*,I_1}  > b_2^{*,upper}$ such that for all $b_2 \geq b_2^{*,I_1}$ and all $s\in [0, T/2]$ we have:
	\begin{equation*}
	\begin{array}{lclclclcl}
		c_u - \zeta_2 &\leq& h_u(b_2,0) &\leq& h_u(b_2,s) &\leq& h_u(b_2, T/2 ) &\leq& c_u + \zeta_2, \\
		c_w - \zeta_2 &\leq& h_w(b_2,0) &\leq& h_w(b_2,s) &\leq& h_w(b_2, T/2 ) &\leq& c_w + \zeta_2.
	\end{array}
	\end{equation*}
	Thus, if $t^* < \frac{T}{2}$, then for any $t \in [0,t^*]$ and $b_2 \geq b_2^{*,I_1}$, we have:
	$$
		\vert h_u(b_2, t) - h_w(b_2,t) \vert^2 \leq  2 [ (c_u + \zeta_2)^2 + (c_w+ \zeta_2)^2 ]\quad \text{and} \quad \int_0^t h_u(b_2,s)ds \geq (c_u - \zeta_2) t.
	$$
	Therefore,
	\begin{IEEEeqnarray}{rCl}
		I_1^{b_2} &\leq& e^{2T(b_1 + \bar{b}_1)}[ (c_u+ \zeta_2)^2 + (c_w + \zeta_2)^2 ] \cdot\frac{2(b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2} \int_0^{t^*} \exp \left(  - \frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot (c_u - \zeta_2) t \right) dt \nonumber \\
		&=& \kappa_1 \left( 1 - e^{ - \kappa_2 (b_2 + \bar{b}_2) t^* } \right), 
	\label{eq:I1_ineq_b2_infinity}
	\end{IEEEeqnarray}
	where the coefficients $ \displaystyle \kappa_1:= \frac{e^{2T(b_1 + \bar{b}_1)}\cdot  [ (c_u+ \zeta_2)^2 + (c_w + \zeta_2)^2 ]}{c_u - \zeta_2}>0$ and $\displaystyle \kappa_2 := \frac{2 (c_u - \zeta_2)}{r + \bar{r}(1-\bar{s})^2}>0$ are independent of $b_2$.	
	In particular, the above inequality is valid when $b_2 = b_2^{*,I_1}$, so if we choose the time point $t^*$ as follows:
	\begin{equation}
	 t^* := \min\left\{ \frac{T}{2}, \  \frac{1}{\kappa_2 \cdot \left( b_2^{*,I_2} + \bar{b}_2\right) } \ln \left( \frac{1}{\displaystyle 1- \frac{\epsilon}{\kappa_1} } \right) \right\},
	\label{eq:t^*_b2_infty} 
	\end{equation}
	then we are able to deduce from inequality (\ref{eq:I1_ineq_b2_infinity}) that: 	(ToDo: there is a mistake here! This is only true for $I_1^{b_2^{*,I_2}}$, not for $I_1^{b_2}$ for any $b_2> b_2^{*,I_2}$.)
	\begin{equation}
		I_1^{b_2} \leq \kappa_1 \left(1 - e^{- \kappa_2 (b_2^{*,I_2} + \bar{b}_2) t^*}  \right) \leq \epsilon.\\
	\label{eq:I1_b2_infty}
	\end{equation}

@@

	Let $b_2^*(\epsilon) := \max \{ b_2^{*,I_1}, b_2^{*,I_2}\}$. Then equations (\ref{eq:I_1_plus_I_2}), (\ref{eq:I1_b2_infty}) and (\ref{eq:I2_b2_infty}) give:
	\begin{equation*}
		\frac{\Delta SC}{SC^{MKV}} \leq \frac{I_1 + I_2}{(b_2 + \bar{b}_2) w_0^{b_2}} \leq \frac{ \epsilon + \epsilon }{h_w(b_2,0)} \leq \frac{2\epsilon}{c_w - \zeta_2}.
	\end{equation*}
	Since the proof holds for arbitrary $\epsilon>0$, we conclude:
	\begin{equation*}
		\lim_{b_2 \to \infty} \frac{\Delta SC}{SC^{MKV}} = 0, 
	\end{equation*}
	and thus,
	$$ \lim_{b_2 \to \infty} PoA = 1.$$

>>>>

% proposition b_2 to \infty
\begin{proposition}
	Assuming (\ref{eq:assumptions}),
	\begin{equation*}
	\begin{split}
	q_T+\bar{q}_T(1-s_T)&>0 \\
	q_T+\bar{q}_T(1-s_T)^2&>0 \\
	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})}&=\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
	\end{split}
	\end{equation*}
	and the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, then:
	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
\label{prop:b2_to_infty}
\end{proposition}

@@

\begin{proof}
	When $b_2 \to \infty$, we have:
	\begin{equation*}
	\begin{array}{l}
	\lambda^{b_2} \to \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}, \\
	B^{b_2} \to \infty, \qquad B^{\eta,b_2} \to \infty\\
	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty},
	\end{array}
	\end{equation*}
	and $A^{u}, (A^{w}, C^w, D^w), (A^{\eta}, C^{\eta}, D^{\eta})$ are independent of  $b_2$. Moreover, we notice that:
	\begin{equation*}
		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} = -\frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{(A^u)^2}{(b_2+\bar{b}_2)^2}+\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \xrightarrow[b_2 \to \infty]{} \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}}.
	\end{equation*}
	and thus, $\delta^{+,b_2}_u - \delta^{-,b_2}_u \xrightarrow[b_2 \to \infty]{} +\infty$.
	From the assumption $q_T+\bar{q}_T(1-s_T)>0$, we have $D^u>0$. From equation (\ref{eq:riccati_ut_sol}), for each $t \in[0,T)$, we deduce:
	\begin{IEEEeqnarray*}{rCl}
		(b_2 + \bar{b}_2) u^{b_2}_t &=& \frac{ \displaystyle  \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{+,b_2}_u}{b_2 + \bar{b}_2}\right) - \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{-,b_2}_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} }
		{\displaystyle \left(\frac{- \delta^{-,b_2}_u}{(b_2 + \bar{b}_2)^2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} \right) + \left(\frac{\delta^{+,b_2}_u}{(b_2 + \bar{b}_2)^2} - \frac{D^{u,b_2} }{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)}  } \nonumber \\
		&&\\
		&\xrightarrow[b_2 \to \infty]{}& \quad (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_u^{b_2 \to \infty}}  =: c_u
	\end{IEEEeqnarray*}
	Idem, for any $t \in [0,T)$,
	$$ (b_2 + \bar{b}_2) w_t^{b_2} \xrightarrow[b_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} = \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} }.$$
	From the assumption:
	\begin{equation*}
	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})}=\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
	\end{equation*}
	we have $c_w=c_u=:c$.

@@

	Fix $\epsilon>0$. In the following, we show that $I_1^{b_2} \leq \epsilon$ and $I_2^{b_2} \leq \epsilon$ for large $b_2$.
	% the term I_1
	First, consider $I_1^{b_2}$. Recall that for $t \in[0,T/2]$, we have $\lim_{b_2 \to \infty}h_u(b_2,t) = c_u$ and $\lim_{b_2 \to \infty}h_w(b_2,t) = c_w$, and for all $b_2 \geq b_2^{*,upper}$, the functions $[0,T/2] \ni s \mapsto u_s^{b_2}$ and $[0,T/2] \ni s \mapsto w_s^{b_2}$ are increasing, and thus, $[0,T/2] \ni s \mapsto h_u(b_2,t)$ and $[0,T/2] \ni s \mapsto h_w(b_2,t)$ are increasing. (Note that $T/2<T$ is chosen arbitrarily, since the above limits do not hold at $T$.) Let $\zeta_2 =\min \{\frac{1}{2}\sqrt{\epsilon c}e^{-T(b_1+\bar{b}_2)},\frac{c}{2}\}$. Then there exists $b_2^{*,I_1}  > b_2^{*,upper}$ such that for all $b_2 \geq b_2^{*,I_1}$ and all $s\in [0, T/2]$ we have:
	\begin{equation*}
	\begin{array}{lclclclcl}
		c - \zeta_2 &\leq& h_u(b_2,0) &\leq& h_u(b_2,s) &\leq& h_u(b_2, T/2 ) &\leq& c + \zeta_2, \\
		c - \zeta_2 &\leq& h_w(b_2,0) &\leq& h_w(b_2,s) &\leq& h_w(b_2, T/2 ) &\leq& c + \zeta_2.
	\end{array}
	\end{equation*}
	Thus, if $t^* < \frac{T}{2}$, then for any $t \in [0,t^*]$ and $b_2 \geq b_2^{*,I_1}$, we have:
	$$
		\vert h_u(b_2, t) - h_w(b_2,t) \vert^2 \leq  4 \zeta_2^2 \quad \text{and} \quad \int_0^t h_u(b_2,s)ds \geq (c - \zeta_2) t \geq \frac{c}{2}\cdot t.
	$$
	Therefore,
	\begin{IEEEeqnarray}{rCl}
		I_1^{b_2} &\leq& 4\zeta_2^2e^{2T(b_1 + \bar{b}_1)} \cdot\frac{(b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2} \int_0^{t^*} \exp \left(  - \frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot \frac{c}{2}\cdot t \right) dt \nonumber \\
		&=& 2\zeta_2^2 \cdot \frac{e^{2T(b_1 + \bar{b}_1)}}{\frac{c}{2}} \left( 1 - e^{ - \frac{2(b_2 + \bar{b}_2) \frac{c}{2}}{r + \bar{r}(1-\bar{s})^2}  t^* } \right) \\
		&\leq& \frac{4e^{2T(b_1 + \bar{b}_1)}}{c}\cdot \zeta_2^2\\
		&\leq&\epsilon, 
	\label{eq:I1_ineq_b2_infinity}
	\end{IEEEeqnarray}
	where the last inequality comes from the definition of $\zeta_2$.

@@

	Let $b_2^*(\epsilon) := \max \{ b_2^{*,I_1}, b_2^{*,I_2}\}$. Then equations (\ref{eq:I_1_plus_I_2}), (\ref{eq:I1_ineq_b2_infinity}) and (\ref{eq:I2_b2_infty}) give:
	\begin{equation*}
		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} \leq \frac{I_1^{b_2} + I_2^{b_2}}{(b_2 + \bar{b}_2) w_0^{b_2}} \leq \frac{ \epsilon + \epsilon }{h_w(b_2,0)} \leq \frac{2\epsilon}{c_w - \zeta_2}.
	\end{equation*}
	Since the proof holds for arbitrary $\epsilon>0$, we conclude:
	\begin{equation*}
		\lim_{b_2 \to \infty} \frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} = 0, 
	\end{equation*}
	and thus,
	$$ \lim_{b_2 \to \infty} PoA^{b_2} = 1.$$
